\documentclass{homework}

\usepackage[table]{xcolor}
\newcommand{\myname}{Kristof Nemeth}
\newcommand{\assignment}{Homework 1}
\newcommand{\duedate}{}
\newcommand{\course}{Coding Theory}

\renewcommand{\C}{\mathcal{C}}
\setcounter{MaxMatrixCols}{29}
\newcommand\y{\cellcolor{gray!30}}

\begin{document}

\begin{problem}
  If we restructure the message into a $11\times 29$ matrix, we can see that
  the ones form the shape of the number $1608$.
  \[
    \begin{pmatrix}
      0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0\\
      0&0&0&\y 1&0&0&0&0&0&\y 1&\y 1&0&0&0&0&\y 1&\y
      1&\y 1&0&0&0&0&\y 1&\y 1&\y 1&0&0&0&0\\
      0&0&\y 1&\y 1&0&0&0&0&\y 1&0&0&0&0&0&\y 1&0&0&0&\y 1&0&0&\y
      1&0&0&0&\y 1&0&0&0\\
      0&\y 1&0&\y 1&0&0&0&\y 1&0&0&0&0&0&0&\y 1&0&0&0&\y 1&0&0&\y
      1&0&0&0&\y 1&0&0&0\\
      0&0&0&\y 1&0&0&\y 1&0&\y 1&\y
      1&\y 1&0&0&0&\y 1&0&0&0&\y 1&0&0&0&\y 1&\y 1&\y 1&0&0&0&0\\
      0&0&0&\y 1&0&0&\y 1&\y 1&0&0&0&\y 1&0&0&\y
      1&0&0&0&\y 1&0&0&\y 1&0&0&0&\y 1&0&0&0\\
      0&0&0&\y 1&0&0&0&\y 1&0&0&0&\y 1&0&0&\y 1&0&0&0&\y 1&0&0&\y
      1&0&0&0&\y 1&0&0&0\\
      0&0&0&\y 1&0&0&0&0&\y 1&\y 1&\y
      1&0&0&0&0&\y 1&\y 1&\y 1&0&0&0&0&\y 1&\y 1&\y 1&0&0&0&0\\
      0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0\\
      0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0\\
      0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0&0\\
    \end{pmatrix}
  \]

  I'm not sure which mathemetician this refers to though.
\end{problem}

\begin{problem}
  Suppose that the binary code $\C$ is an  $(n,M,d)$ code. Prove that
  \begin{itemize}
    \item If $s \le d-1$, then $C$ can detect up to $s$ errors in any codeword.

      Let $c \in \C$ be a codeword, and let $\epsilon$ have weight $s>0$. Let
      $c_2
      \in \C, c_2 \ne c$ Then
      \[d(c+\epsilon,c_2)
        \ge d(c_2,c)-d(c,c+\epsilon) \ge d-s \ge 1
      \]
      Hence, $c+\epsilon$ is not a codeword in $C$, and we can detect that an
      error has occured.
    \item If $2t \le d-1$, then $C$ can correct up to $t$ errors in any codeword.

      Let $c \in \C$ be a codeword, and let $\epsilon$ have weight $t > 0$. Let
      $c_2 \in C, c_2 \ne c$. We can can then calculate
      \[
        d(c_2,c+\epsilon) \ge d(c,c_2) - d(c,c+\epsilon) \ge d - t \ge (2t + 1)
        - t = t + 1 > t = d(c,c+\epsilon)
      \]
      Hence, if there are  $t$ or fewer errors, $c+\epsilon$ is closer to $c$
      than any other codeword in $\C$, and therefore, the errors can be
      corrected.
  \end{itemize}
\end{problem}

\begin{problem}
  Let $\C$ be the linear binary code whose parity check matrix is
  \[
    A =
    \begin{pmatrix}
      1&0&1&1&0&0&0 \\
      0&1&0&0&1&0&1 \\
      0&1&1&0&0&1&1 \\
      1&1&1&0&0&0&0
    \end{pmatrix}
  \]
  \begin{itemize}
    \item Find a generator matrix of the code

      We are looking for a basis of the null space of $A$. We start by putting $A$ into
      row echelon form

      \[ \bar{A} =
        \begin{pmatrix}
          1&0&0&0&0&1&1 \\
          0&1&0&0&1&0&1 \\
          0&0&1&0&1&1&0 \\
          0&0&0&1&1&0&1
        \end{pmatrix}
      \]
      Then $\bar{A}$ is in the form
      $\begin{pmatrix}
        I | P
      \end{pmatrix}$. Then a basis for the null space of this matrix is given by
      $G = \begin{pmatrix}
        P^\perp | I
      \end{pmatrix}$
      So
      \[ G =
        \begin{pmatrix}
          0&1&1&1&1&0&0 \\
          1&0&1&0&0&1&0 \\
          1&1&0&1&0&0&1 \\
        \end{pmatrix}
      \]
    \item
      The matrix with its all the codewords as rows is
      \[
        \begin{pmatrix}
          0&0&0&0&0&0&0\\
          0&1&1&1&1&0&0\\
          1&0&1&1&0&1&0\\
          1&1&0&0&1&1&0\\
          1&0&1&1&0&1&0\\
          1&0&0&1&1&0&1\\
          0&1&0&1&0&1&1\\
          0&0&1&0&1&1&1\\
        \end{pmatrix}
      \]
    \item The code represents $3$ bit messages as $7$ bit codewords, and the
      minimum (non-zero) weight is $4$ so this is
      a $[7,3,4]$ code.

    \item
      The covering radius of the code is 2, since the maximum distance between
      any two codewords is also $4$.

    \item
      The minimum weight of the code is $4$, so this code can correct $1$ error,
      and can detect up to $3$ errors.
  \end{itemize}
\end{problem}

\begin{problem}
  Let $C$ be a binary linear code, and $H$ be the parity check matrix for $C$.
  Then for a codeword $c$, we have $Hc = 0$. Let $\bar{c} = c + \epsilon$ for
  some error  $\epsilon$. Then \[
    H\bar{c} = H(c+\epsilon) = Hc+H\epsilon = H\epsilon
  \]
  Hence, the syndrome of $\bar{c}$ is the same as the syndrome of the error
  itself. Furthermore, we can decompose the error $\epsilon$ into the
  sum of vectors of weight $1$, where $\epsilon_n$ represents the vector of
  weight one with a $1$ in column $n$. Then
  \[
    H\epsilon = H{\sum\limits_{n=1}^{N} \epsilon_n} =
    {\sum\limits_{\epsilon_n=1}^{} H\epsilon_n}
  \]
\end{problem}
\begin{problem}
  Let $C+\epsilon$ be a coset of the code $\C$ in the carrier space $V$. Let $x
  \in C+\epsilon$, which means that $x = c + \epsilon$ for some $c \in C$. Then
  the syndrome of  $x$ is $Hx = H(c+\epsilon) = Hc+H\epsilon=H\epsilon$. Now let
  $x \in V$, and $Hx$ be the syndrome of $x$. Let $y \in V$ such that $Hx = Hy$.
  Then $Hx = H\epsilon_x = H\epsilon_y = Hy$, and so  $C+\epsilon_x =
  C+\epsilon_y$. Hence, there is a 1-1 correspondence between syndromes and
  cosets.
\end{problem}

\begin{problem}
  In order for a decoder error to occur for the code $C$ in problem 3, at
  least two single
  bit errors must be introduced into a codeword.

  Hence, the probability of a decoder error is \[
    {\sum\limits_{n=2}^{7} }p^n(1-p)^{7-n}{{7}\choose{n}}=
    1- \left(p^0(1-p)^7{{7}\choose{0}} + p^1(1-p)^6{{7}\choose{1}}\right)=
    1 - 0.999^7+(0.001)(0.999^6)7 = 0.013937
  \]
\end{problem}
\begin{problem}
  Let $C$ be a $t$-error correcting binary code of length $n$, containing
  $M$ codewords. Let $\epsilon$ have weight $i$. Then there are exactly
  ${n}\choose{i}$ possible errors $\epsilon$ with that weight. And so the total
  number of words that differ from a codeword $c$ by less than or equal to $t$
  errors is \[
    M\left(1+ {{n}\choose{1}}+\cdots+{{n}\choose{t}}\right)
  \]
  Clearly, if this number is greater than $2^n$, then we have more words than
  there are words in the carrier space, which is a contradiction.
\end{problem}
\begin{problem}
In order for $C$ to be a perfect code, we must have 
\[
    M\left(1+ {{n}\choose{1}}+\cdots+{{n}\choose{t}}\right) = 2^n
\] 
That is, if for all $M$ codewords we have a sphere of radius $t$, the union of
all of the resultiong words is the whole space $V$.

By brute force, and by filtering out all of the trivial codes where $d<3$, we
have the list of all perfect codes where $n\le 100$:

[3,2,3]
[5,2,5]
[7,16,3]
[7,16,4]
[7,2,7]
[9,2,9]
[11,2,11]
[13,2,13]
[15,2048,3]
[15,2048,4]
[15,2,15]
[17,2,17]
[19,2,19]
[21,2,21]
[23,4096,7]
[23,4096,8]
[23,2,23]
[25,2,25]
[27,2,27]
[29,2,29]
[31,67108864,3]
[31,67108864,4]
[31,2,31]
[33,2,33]
[35,2,35]
[37,2,37]
[39,2,39]
[41,2,41]
[43,2,43]
[45,2,45]
[47,2,47]
[49,2,49]
[51,2,51]
[53,2,53]
[55,2,55]
[57,2,57]
[59,2,59]

\end{problem}
\end{document}
